\documentclass[twocolumn,superscriptaddress,prd]{revtex4-1} 

\pdfoutput=1 

%\usepackage{hyperref}
\usepackage{verbatim}
%\usepackage[font=normalsize]{caption}
\usepackage{mathtools}
\usepackage{relsize}
\usepackage{natbib}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[capposition=bottom]{floatrow}
\usepackage{amssymb}
\usepackage{graphicx}
%\usepackage{caption}
\usepackage{rotating}
\usepackage{afterpage}
\usepackage{float}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{epstopdf}

\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{color}
\usepackage{array}
\usepackage{multirow}
\usepackage{wasysym}
\usepackage{verbatim}
\usepackage{subfig}


%switch from two to one column



\addtolength{\oddsidemargin}{-.500in}
\addtolength{\evensidemargin}{-.375in}
\addtolength{\textwidth}{1.00in}
%\addtolength{\voffset}{-70pt}
%\addtolength{\textheight} {120pt}
\newcommand{\isot}[2]{$^{#2}$#1 }
\newcommand{\xeiso}{\isot{Xe}{136}}
\newcommand{\thsrc}{\isot{Th}{228}}
\newcommand{\cosrc}{\isot{Co}{60}}
\newcommand{\krsrc}{\isot{Kr}{83m}}
\newcommand{\cssrc}{\isot{Cs}{137}}
\newcommand{\kevee}{keV$_{ee}$ }
\newcommand{\nonubb}  {$0\nu \beta \beta$}
\newcommand{\gone}{$0.116 \pm 0.003$}
\newcommand{\gtwo}{$11.41 \pm 0.52$}
\newcommand{\fixit}[1]{{\color{red}#1}} 

\renewcommand\thesection{\Roman{section}.}
\renewcommand\thesubsection{\arabic{subsection}.}
\renewcommand\thesubsubsection{\alph{subsubsection}.}
\titleformat{\section}[block]{\bfseries\filcenter}{\thesection}{1em}{}
\titleformat{\subsection}[block]{\bfseries\filcenter}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\bfseries\filcenter}{\thesubsubsection}{1em}{}

\usepackage{titlesec}

%\titleformat{\section}{\bfseries\filcenter}{\thesubsection}{1em}{}
%\titleformat{\subsection}{\bfseries\filcenter}{\thesubsection}{1em}{}
%\titleformat*{\paragraph}{\large\bfseries}
%\titleformat*{\subparagraph}{\large\bfseries}

\begin{document}

\title{Run04 corrections}

\input{authors}

\input{Abstract}

%\twocolumn[\maketitle]
		\maketitle


\input{Introduction}

\input{procedure}

\input{Results}

\input{Summary}

\appendix

%\input{Appendix}


\begin{acknowledgments}

This work was partially supported by the U.S. Department of Energy (DOE) under award numbers DE-FG02-08ER41549, DE-FG02-91ER40688, DE-FG02-95ER40917, DE-FG02-91ER40674, DE-NA0000979, DE-FG02-11ER41738, DE-SC0006605, DE-AC02-05CH11231, DE-AC52-07NA27344, and DE-FG01-91ER40618; the U.S. National Science Foundation under award numbers PHYS-0750671, PHY-0801536, PHY-1004661, PHY-1102470, PHY-1003660, PHY-1312561, PHY-1347449; the Research Corporation grant RA0350; the Center for Ultra-low Background Experiments in the Dakotas (CUBED); and the South Dakota School of Mines and Technology (SDSMT). LIP-Coimbra acknowledges funding from Funda\c{c}\~{a}o para a Ci\^{e}ncia e a Tecnologia (FCT)   through the project-grant PTDC/FIS-NUC/1525/2014. Imperial College and Brown University thank the UK Royal Society for travel funds under the International Exchange Scheme (IE120804). The UK groups acknowledge institutional support from Imperial College London, University College London and Edinburgh University, and from the Science \& Technology Facilities Council for PhD studentship ST/K502042/1 (AB). The University of Edinburgh is a charitable body, registered in Scotland, with registration number SC005336. This research was conducted using computational resources and services at the Center for Computation and Visualization, Brown University.

We gratefully acknowledge the logistical and technical support and the access to laboratory infrastructure provided to us by the Sanford Underground Research Facility (SURF) and its personnel at Lead, South Dakota. SURF was developed by the South Dakota Science and Technology Authority, with an important philanthropic donation from T. Denny Sanford, and is operated by Lawrence Berkeley National Laboratory for the Department of Energy, Office of High Energy Physics.

\end{acknowledgments}


%double blank page so that the table doesn't spill into the bibliography
\newpage
\thispagestyle{empty}
\mbox{}
\newpage
\thispagestyle{empty}
\mbox{}

%\input{Tritium.bbl}

\bibliography{KrypCal_Paper}

\end{document}